Age-related changes in plant growth and traits

### 2016-01-15 Accessory_figs_2016.Rmd
work on accessory cost manuscript figures

win.metafile("figs2/seedset_vs_accessory.wmf", height=6, width=6)
plot

@@

plot(accessory_per_seed~seedset,data=subset(SummaryInd,accessory_per_seed>0&seedset>0&age>2),col=col.spp(species),pch=16,log="xy")
points(accessory_per_seed~seedset,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&seedset>0),col="black",pch=16,cex=2.5)
points(accessory_per_seed~seedset,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&seedset>0),col=col.spp(species),pch=16,cex=2)
mod <- lm(log10(accessory_per_seed)~log10(seedset),data=subset(SummarySpp[["mean"]]))
words.top.right.logxy(mod)
for(i in 1:14) {
abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
}
abline(coef(mod)[1],coef(mod)[2],lwd=3)
legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
dev.off()
```

@@

>>>>

@@

plot(accessory_per_seed~seedset,data=subset(SummaryInd,accessory_per_seed>0&seedset>0&age>2),col=col.spp(species),pch=16,log="xy")
points(accessory_per_seed~seedset,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&seedset>0),col="black",pch=16,cex=2.5)
points(accessory_per_seed~seedset,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&seedset>0),col=col.spp(species),pch=16,cex=2)
mod <- lm(log10(accessory_per_seed)~log10(seedset),data=subset(SummarySpp[["mean"]]))
words.top.right.logxy(mod)
for(i in 1:14) {
abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
}
abline(coef(mod)[1],coef(mod)[2],lwd=3)
legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
#dev.off()
```

@@

###RA not correlated with accessory costs
```{r}
xvar <- "RA"
yvar <- "accessory_per_seed"

data <- subset(SummaryInd,accessory_per_seed>0&RA>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  ((x[[xvar]]))))
results <- summarise_all_fits(lmfits)

plot(accessory_per_seed~RA,data=subset(SummaryInd,accessory_per_seed>0&RA>0&age>2),col=col.spp(species),pch=16,log="y")
points(accessory_per_seed~RA,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&RA>0),col="black",pch=16,cex=3)
points(accessory_per_seed~RA,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&RA>0),col=col.spp(species),pch=16,cex=2)
mod <- lm(log10(accessory_per_seed)~(RA),data=subset(SummarySpp[["mean"]]))
words.top.right.logx(mod)
for(i in 1:14) {
abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
}
abline(coef(mod)[1],coef(mod)[2],lwd=3)
legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
```

```{r}
xvar <- "repro_inv"
yvar <- "accessory_per_seed"

data <- subset(SummaryInd,accessory_per_seed>0&repro_inv>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

plot(accessory_per_seed~repro_inv,data=subset(SummaryInd,accessory_per_seed>0&repro_inv>0&age>2),col=col.spp(species),pch=16,log="xy")
points(accessory_per_seed~repro_inv,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&repro_inv>0),col="black",pch=16,cex=3)
points(accessory_per_seed~repro_inv,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&repro_inv>0),col=col.spp(species),pch=16,cex=2)
mod <- lm(log10(accessory_per_seed)~log10(repro_inv),data=subset(SummarySpp[["mean"]]))
words.top.right.logxy(mod)
for(i in 1:14) {
abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
}
abline(coef(mod)[1],coef(mod)[2],lwd=3)
legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
```

```{r}
xvar <- "age"
yvar <- "accessory_per_seed"

data <- subset(SummaryInd,accessory_per_seed>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results
write.csv(results, file="figs2/age_vs_accessory.csv",row.names=FALSE)

par(mfrow=c(1,2), cex=1, omi=c(1,1,.1,.1), mai=c(1,1,.5,.5))

plot(accessory_per_seed~age,data=subset(SummaryInd,accessory_per_seed>0&age>0&age>2&species!="COER"),col=col.spp(species),pch=16,log="xy")

for(i in 1:14) {
abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
}
legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
```

```{r}
xvar <- "age"
yvar <- "seedset"

data <- subset(SummaryInd,seedset>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results
#write.csv(results, file="figs2/age_vs_accessory.csv",row.names=FALSE)

#par(mfrow=c(1,1), cex=1, omi=c(1,1,.1,.1), mai=c(1,1,.5,.5))

plot(seedset~age,data=subset(SummaryInd,seedset>0&age>2),col=col.spp(species),pch=16,log="xy")

for(i in 1:14) {
abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
}
legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
```

```{r}
xvar <- "age"
yvar <- "seed_count"

data <- subset(SummaryInd,seedset>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results
#write.csv(results, file="figs2/age_vs_accessory.csv",row.names=FALSE)

#par(mfrow=c(1,1), cex=1, omi=c(1,1,.1,.1), mai=c(1,1,.5,.5))

plot(seed_count~age,data=subset(SummaryInd,seedset>0&age>2),col=col.spp(species),pch=16,log="xy")

for(i in 1:14) {
abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
}
legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
```

```{r}
xvar <- "age"
yvar <- "c_div_p"

data <- subset(SummaryInd,c_div_p>0&age>2&species!="COER")
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results
```

```{r}
xvar <- "seedset"
yvar <- "b_div_p"

data <- subset(SummaryInd,b_div_p>0&seedset>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

# extra1 <- select(SummarySpp[["max"]],species,seedset)
# names(extra1) <- c("species","seedset_max")
# extra2 <- select(SummarySpp[["min"]],species,seedset)
# names(extra2) <- c("species","seedset_min")
# 
# results <- merge(results, extra1, by="species", all=TRUE)
# results <- merge(results, extra2, by="species", all=TRUE)
# results$seedset_min <- 0.0001
# 
# results$max_y <- (10^(results$seedset_max*results$b))*10^(results$a)
# results$min_y <- (10^(results$seedset_min*results$b))*10^(results$a)

#write.csv(results, file="figs2/age_vs_accessory.csv",row.names=FALSE)

plot(b_div_p~seedset,data=subset(SummaryInd,b_div_p>0&seedset>0),col=col.spp(species),pch=16,log="xy")

#View(results)

for(i in 1:14) {
#arrows(results[i,8],results[i,10],results[i,7],results[i,9],col=col.spp(results$species[i]),code=0,lwd=2)  
abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
}
legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
```

```{r}
xvar <- "total_weight"
yvar <- "repro_all_count"

data <- subset(SummaryInd,repro_all_count>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

plot(repro_all_count~total_weight,data=subset(SummaryInd,repro_all_count>0&age>2&total_weight>0),col=col.spp(species),pch=16,log="xy")
points(repro_all_count~total_weight,data=subset(SummarySpp[["mean"]],repro_all_count>0&total_weight>0),col="black",pch=16,cex=3)
points(repro_all_count~total_weight,data=subset(SummarySpp[["mean"]],repro_all_count>0&total_weight>0),col=col.spp(species),pch=16,cex=2)
mod <- lm(log10(total_weight)~log10(repro_all_count),data=subset(SummarySpp[["mean"]]))
words.top.right.logxy(mod)
for(i in 1:14) {
  abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
}
abline(coef(mod)[1],coef(mod)[2],lwd=3)
legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
```

```{r}
xvar <- "total_weight"
yvar <- "repro_inv"

data <- subset(SummaryInd,repro_inv>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

plot(repro_inv~total_weight,data=subset(SummaryInd,repro_inv>0&age>2&total_weight>0),col=col.spp(species),pch=16,log="xy")
points(repro_inv~total_weight,data=subset(SummarySpp[["mean"]],repro_inv>0&total_weight>0),col="black",pch=16,cex=3)
points(repro_inv~total_weight,data=subset(SummarySpp[["mean"]],repro_inv>0&total_weight>0),col=col.spp(species),pch=16,cex=2)
mod <- lm(log10(total_weight)~log10(repro_inv),data=subset(SummarySpp[["mean"]]))
words.top.right.logxy(mod)
for(i in 1:14) {
  abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
}
abline(coef(mod)[1],coef(mod)[2],lwd=3)
legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
```

```{r}
xvar <- "total_weight_0"
yvar <- "propagule_inv"

data <- subset(SummaryInd,propagule_inv>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

plot(propagule_inv~total_weight_0,data=subset(SummaryInd,propagule_inv>0&age>2&total_weight_0>0),col=col.spp(species),pch=16,log="xy")
points(propagule_inv~total_weight_0,data=subset(SummarySpp[["mean"]],propagule_inv>0&total_weight_0>0),col="black",pch=16,cex=3)
points(propagule_inv~total_weight_0,data=subset(SummarySpp[["mean"]],propagule_inv>0&total_weight_0>0),col=col.spp(species),pch=16,cex=2)
mod <- lm(log10(total_weight_0)~log10(propagule_inv),data=subset(SummaryInd,propagule_inv>0&age>2&total_weight_0>0))
words.top.right.logxy(mod)
for(i in 1:14) {
  abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
}
#abline(coef(mod)[1],coef(mod)[2],lwd=3)
legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
```
